The evolution of gene expression in the term placenta of viviparous mammals

### 2015-10-13 manuscript/manuscript.Rnw
add a more complete expression function to make printing expression easier

<<top.genes.function,echo=FALSE,results="hide">>=
top.genes.table <- function(species.name,n=50) {
    temp <- 
        combined.fpkm[species==species.name &
                          !(human_name %in% housekeeping.genes.superset[,gene_short_name]) &
                              !grepl("(RNA\\d|MT)-",human_name)
                      ][order(-mean_fpkm)][!duplicated(gene_short_name)][1:n,list(gene_short_name,
                                                                                  human_name,mean_fpkm)]
    setnames(temp,c("Gene name","Human Name","FPKM"))
    if (species.name=="homo sapiens") {
        temp <- temp[,-2,with=FALSE]
    }
    return(temp)
}
gene.expression <- function(species.name,gene) {
    combined.fpkm[species==species.name &
                      gene_short_name==gene,mean_fpkm]
}

>>>>

<<top.genes.function,echo=FALSE,results="hide">>=
top.genes.table <- function(species.name,n=50) {
    temp <- 
        combined.fpkm[species==species.name &
                           !(!is.na(human_name) & 
                                 human_name %in% housekeeping.genes.superset[,gene_short_name]) &
                               !grepl("((RNA\\d|MT)-|^RPS\\d+$)",human_name) &
                                   !grepl("(^MT-|^RP[LS]\\d+[ABCD]?(?:-.+)?$|rRNA$)",gene_short_name)
                      ][order(-mean_fpkm)][,list(name_or_id,
                                                 human_name,mean_fpkm)]
    temp <- temp[!duplicated(name_or_id)][1:n]
    setnames(temp,c("Gene name","Human Name","FPKM"))
    if (species.name=="homo sapiens") {
        temp <- temp[,-2,with=FALSE]
    }
    return(temp)
}
gene.expression <- function(species.name,gene,complete=FALSE) {
    fpkm <- combined.fpkm[species==species.name &
                              gene_short_name==gene,
                          mean_fpkm]

    if (complete) {
        return(paste0("\\textit{",gene,"}=",
                      formatC(fpkm,digits=2,format="f"),
                      " \\ac{FPKM}"
                      ))
    } else {
        return(fpkm)
    }
}
